hbm_paper_results

### 2024-06-10 paper_lbcc_results.Rmd
cleaning up
cohens fsq for unharmonized brain charts

Cohen's F squared for study effects

```{r}
gam_centile_f2 <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-log-cf-cf.gam-batch.study-data_cohenfsq.csv"))
gam_centile_f2$combat <- "ComBat-GAM"

@@

f2.df <- rbind(gam_centile_f2, gamlss_centile_f2)
f2.df <- f2.df %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))
```

@@

```{r}
fsq_plt <- ggplot(f2.df) +
  geom_col(aes(x=pheno, y=fsq, fill=combat), position="dodge") + 
  facet_wrap(~pheno_cat, scales="free") +
  theme_linedraw() +
  theme(axis.text.x = element_blank(), legend.position="bottom", axis.ticks.x = element_blank()) + 
  scale_fill_manual(values = c('ComBat-GAM' = "#3D75C2", ComBatLS ="#CFB023FF"), name = "ComBat Configuration") +
  labs(y="Effect Size (Cohen's F-Squared)", x = "Brain Feature")
ggsave("figs/cohens_fsq.jpeg", fsq_plt)
```

```{r}
f2.df.sum <- f2.df %>%
  group_by(pheno) %>%
  arrange(combat) %>%
  mutate(F2_diff = fsq - fsq[1]) #gamlss - gam value, + number means site effect is larger in combatLS

>>>>

##Cohen's F-squared for study effects

```{r}
raw_centile_f2 <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-raw_cohenfsq.csv"))
raw_centile_f2$combat <- "Unharmonized"

gam_centile_f2 <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-log-cf-cf.gam-batch.study-data_cohenfsq.csv"))
gam_centile_f2$combat <- "ComBat-GAM"

@@

f2.df <- rbind(raw_centile_f2, gam_centile_f2, gamlss_centile_f2)
f2.df <- f2.df %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

unique(f2.df$combat)

f2.df %>%
  group_by(combat) %>%
  summarize(median = median(fsq),
            IQR = IQR(fsq))
```

@@

```{r}
fsq_plt <- ggplot(f2.df) +
  geom_col(aes(x=pheno, y=fsq, fill=combat), position="dodge") + 
  facet_wrap(~pheno_cat, scales="free") +
  theme_linedraw() +
  theme(axis.text.x = element_blank(), legend.position="bottom", axis.ticks.x = element_blank()) + 
  scale_fill_manual(values = c('ComBat-GAM' = "#3D75C2", ComBatLS ="#CFB023FF", Unharmonized = "darkgray"), name = "Harmonization") +
  labs(y="Effect Size (Cohen's F-Squared)", x = "Brain Feature")
ggsave("figs/cohens_fsq.jpeg", fsq_plt)
```

```{r}
f2.df.sum <- f2.df %>%
  dplyr::filter(combat != "Umharmonized") %>%
  group_by(pheno) %>%
  arrange(combat) %>%
  mutate(F2_diff = fsq - fsq[1]) #gamlss - gam value, + number means site effect is larger in combatLS
